Ontologien aus dem Bereich der Industrie (TODO)

### 2024-03-04 paper.tex
added further (potentially relevant) ontologies using Github search
https://github.com/search?q=topic%3Aontology+industry&type=repositories&ref=advsearch

@@

@@

\subsection{Collaborative Manufacturing Services Ontology}

@@

\subsubsection{IFC4\_ADD1}

@@

@@

@@

\subsubsection{Smart Applications REFerence Ontology (SAREF)}

@@

\subsubsection{Smart Applications REFerence Ontology extension for building (SAREF4BLDG)}

@@

\subsubsection{Smart Applications REFerence Ontology extension for industry and manufacturing (SAREF4INMA)}

>>>>

- Github Suche (nur Einträge auf Englisch): https://github.com/search?q=topic%3Aontology+industry&type=repositories&ref=advsearch&p=1
  - Topic: ontology
  - Suchbegriffe: industry, manufacturing

@@

\subsubsection{Automotive Industry Ontology}

Automotive Industry Ontology

https://github.com/iurianu/auto-ontology/tree/master

Frage an Autor ob Projekt noch forgesetzt wird: https://github.com/iurianu/auto-ontology/issues/1

@@

\subsubsection{Capability and Skill Ontology (CaSk)}

"OWL ontology to describe capabilities and skills of things. [...] In the context of automated production, Capabilities and Skills are terms that are used to refer to machine functions."

https://github.com/CaSkade-Automation/CaSk

\subsubsection{COGITO Safety Ontology}

https://github.com/oeg-upm/cogito-safety-ontology/tree/main

Prüfe, ob das für uns relevant ist. Projekt fiel mit im Kontext von https://github.com/mahsa-teimourikia/Safety-Ontology auf.

\subsubsection{Collaborative Manufacturing Services Ontology}

@@

\subsubsection{ifcOWL}

@@

\subsubsection{Ontology-based Customization and Visualization of Information Flow control in an Industry 4.0 scenario ????}

Könnte relevant sein, weil auf der README ein paar Ontologien im Kontext von Industrie 4.0 erwähnt werden: \url{https://github.com/ko3n1g/Ontology-based-InformationFlow-Industry-4.0?tab=readme-ov-file#ontologies}

@@

\subsubsection{Safety Ontology}

"This is an ontology for extracting the safety knowledge in industry 4.0."

https://github.com/mahsa-teimourikia/Safety-Ontology

@@

\subsubsection{Smart Applications Reference Ontology (SAREF)}

@@

\subsubsection{Smart Applications Reference Ontology extension for building (SAREF4BLDG)}

@@

\subsubsection{Smart Applications Reference Ontology extension for industry and manufacturing (SAREF4INMA)}
